The problem and promise of scale in multilayer networks

### 2020-02-04 paper/manuscript.Rmd
ref
catching a few typos

(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals varied dramatically depending on the lenght of the time window <!--TODO:**[JWT: previously this was describing fig. 3. I don't know if what I wrote best encapsulates what connnective redundancy does here. Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance benerally increased during the summer months but was relatively stable across time window lengths for each landcover layer. D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. <!--TODO:**[see if you agree with my changes. B-D were based off fig. 3 and not relevant to this figure]**-->

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been been considered in describing the causes and consequences of the
social environment in the context of (1) Individual fitness and phenotypes
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode et al. 2011), 
and (3) habitat selection and space use (He et al. 2019).
Here, we explore how mutlilayer networks may apply to these emerging fields to
contribute to the development of social network theory and application.

@@

Animal movement undoubtedly affects an individual's social environment
[@Strandburg-Peshkin2015]. Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al. 2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al. 2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g. Mourier et al. 2019).

>>>>

(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. B) Mean connective redundancy across individuals varied dramatically depending on the length of the time window <!--TODO:**[JWT: previously this was describing fig. 3. I don't know if what I wrote best encapsulates what connnective redundancy does here. Length of time window seems to make connective redundancy highly variable as it changes.]**.--> C) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer. D) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. <!--TODO:**[see if you agree with my changes. B-D were based off fig. 3 and not relevant to this figure]**-->

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been considered in describing the causes and consequences of the
social environment in the context of (1) Individual fitness and phenotypes
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode et al. 2011), 
and (3) habitat selection and space use (He et al. 2019).
Here, we explore how mutlilayer networks may apply to these emerging fields to
contribute to the development of social network theory and application.

@@

Animal movement undoubtedly affects an individual's social environment
[@Strandburg-Peshkin_2015]. Movement is a dynamic process that is related
to the resources an individual consumes within their home range and the space
that they use (Van Moorter et al. 2016). Collective movement can reduce
group-level predation via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
(Jolles et al. 2019). Social processes, movement decisions, and space use are
inextricably linked and multilayer networks represent a potential analytical
framework for linking these processes (e.g. Mourier et al. 2019).
